NumPy---Array Programming in Python

### 2020-01-11 body.tex
Add caption for Fig. 2: Reductions

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{static/sketches/reductions}
  \caption{\textbf{Reductions.} \fixme{Reducing an array along one of several axes. Note:
  may want to fix to have right-hand axis system.}
   }
  \label{fig:reductions}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{static/sketches/reductions}
  \caption{\textbf{Reductions.} Reduction operations act along one or more axes. In this example, a three-dimensional array is shown to be summed along various single axes to produce two-dimensional results, or along two axes consecutively to produce a one-dimensional result. \fixme{May want to fix to have right-hand axis system.}
   }
  \label{fig:reductions}
\end{figure}
